Modelling biological pathway dynamics\\with \tas

### 2013-07-05 Paper.tex
Updated Q&A. Added CellIllustrator and other minor corrections to the paper

A third level of abstraction is the discretization of activities into integer variables with a user-defined granularity, ranging from Boolean (2 levels) 
to almost continuous (100 levels). This discretization gives the user the flexibility to adjust the model abstraction to the level of 
prior knowledge, to the quality and nature of experimental data and to the biological questions at hand. It also allows 
control over the trade-off between level of detail and computational performance for large models.

@@

Tools that allow to construct models based on ODEs include for example COPASI~\cite{copasi}, 
E-Cell~\cite{e-cell} and GNA~\cite{gna}.
These tools add to the potential of ODEs by coupling them with additional modelling approaches,
such as stochastic models\footnote{Stochastic modelling becomes particularly useful when some
molecular species have very small concentrations, which nullifies the assumption of a well-mixed solution used in models based on ODEs.}
used in COPASI and E-Cell, and by allowing for qualitative modelling, as does GNA.
Other tools, such as Systems Biology Workbench~\cite{sbw}, allow to couple high-performance
analysis engines (such as roadRunner) to user-friendly interfaces (e.g. JDesigner). Finally, tools such as CellDesigner~\cite{celldesigner}
provide an appealing graphical representation as an interface to powerful computational engines.
Most of the cited tools are founded on parameter-intensive approaches, while the paradigm implemented in ANIMO
uses less precise formulations, which requires less initial knowledge from the user.

>>>>

A third level of abstraction is the discretization of activities into integer variables with a user-defined granularity, ranging from Boolean (2 levels) 
to almost continuous (100 levels). This discretization gives the user the flexibility to adjust the model abstraction to the level of 
prior knowledge, to the quality and nature of experimental data and to the biological questions at hand.
A beginner working on smaller models will profit from choosing a high granularity, while
an expert ANIMO user will be able to keep a balance between level of detail and computational performance when dealing with large models.

@@

Tools that allow to construct models based on ODEs include for example COPASI~\cite{copasi}, 
E-Cell~\cite{e-cell} and GNA~\cite{gna}.
These tools add to the potential of ODEs by coupling them with additional modelling approaches,
such as stochastic models\footnote{Stochastic modelling becomes particularly useful when some
molecular species have very small concentrations, which nullifies the assumption of a well-mixed solution used in models based on ODEs.}
used in COPASI and E-Cell, and by allowing for qualitative modelling, as does GNA.
Other tools, such as Systems Biology Workbench~\cite{sbw}, allow to couple high-performance
analysis engines (such as roadRunner) to user-friendly interfaces (e.g. JDesigner). Finally, tools such as CellDesigner~\cite{celldesigner}
and Cell Illustrator~\cite{cell-illustrator}
provide an appealing graphical representation as an interface to powerful computational engines.
Most of the cited tools are founded on parameter-intensive approaches, while the ANIMO's paradigm
uses less precise formulations, thus requiring less initial knowledge from the user.
